% ----------------------------------------------------------------
\cventry
    {Full Stack Engineer} % Position
    {FPT Information System} % Institution
    {Ho Chi Minh City} % Location
    {11/2019 - 4/2020} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Goal: Worked closely with other developers and Project Managers to plan and launch features related to the financial systems of web-enabled services.}
        \item {Project: Task management (A task management system, ensuring the main functions: assigning tasks – getting tasks – completing assigned tasks – responding to assignors. In addition, the system also provides functions statistics and reports the weekly task progress cycle.). Team size: 4}
        \item {Responsibilities: }
        {
            \begin{itemize} % Item(s)
                \item {Configure Single Sign On (SSO) for BA Online system of FPT Information System (FIS).}
                \item {Write SRS document for Task Management.}
                \item {Built UI Task Management by Angular 8.0 Framework.}
                \item {Handle all of API for Task Management (Create – Update – Delete – Copy - Move) using Spring Boot.}
                \item {Handle Security for Task Management using Spring Security.}
                \item {Integrated synchronization with all employee accounts in FIS into the Task Management system.}
            \end{itemize}
        }
        \item {Skills: Microservices · RabbitMQ · ActiveMQ · Redis · Docker · Spring Batch · Java · Spring Data · Angular · MySQL · MongoDB · Spring Framework · Spring Security}
      \end{cvitems}
    }
% ----------------------------------------------------------------