  \cventry
    {Backend Software Engineer} % Position
    {Neyu Corporation} % Institution
    {Ho Chi Minh City} % Location
    {5/2020 - now} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Goal: Worked closely with other developers to plan and launch features related to the Telesale system of web-enabled services.}
        \item { Project: \textbf{Telesale (TMS)}, team size: all of developers. Develop new applications, components and functions for existing systems. Investigating alternate configurations and implementing better solutions. }
        % {
        %     \begin{itemize}
        %         \item { Develop new applications, components and functions for existing systems. }
        %         \item { Investigating alternate configurations and implementing better solutions. }
        %     \end{itemize}
        % }
        \item { Project: \textbf{Contact Center Management (CCM)}, team size: 4 }
        {
            \begin{itemize}
                \item {Using Asterisk Server (FreePBX), building a web app directly and using client apps such as Microsip or Zoipier5 to connect to the switchboard.}
                \item { Call system and customer care, monitor the real-time status of sales calls to customers. }
                \item { Provide valuable reports on the call quality between customers and sales. }
            \end{itemize}
        }
        \item { Project: \textbf{Logistic Management}, team size: 10 }
        {
            \begin{itemize}
                \item { System for managing last-mile partners, fulfillment (3PLs), and address locations. }
                \item { Mapping the location between integrated 3PLs units. }
                \item { Routing delivery units for orders upon successful order placement. }
                \item { Integrated last-mile 3PLs: GHN Express (Vietnam), DHL (Vietnam, Thailand, Indonesia), NinjaVan (Vietnam, Indonesia), Topship (Vietnam), Shopee Express (Vietnam, Thailand), Lion Parcel (Indonesia), Flash (Malaysia). }
                \item { Integrated fulfillment 3PLs: Baspro (Vietnam), Boxme (Vietnam, Thailand, Indonesia, Malaysia, Philippines). }
            \end{itemize}
        }
        \item { Project: \textbf{System Management}, team size: 7 }
        { 
            \begin{itemize}
                \item { User management system. }
                \item { Team management system. }
                \item { Sales campaign management system. }
                \item { User permission management system. }
            \end{itemize}
        }
        \item { Project: \textbf{Workforce Management (WFM)}, team size: 7 }
        {
            \begin{itemize}
                \item { Management of sales work quality. }
                \item { Management of sales customer care quality. }
                \item { Management of sales quality. }
                \item { The attendance management of sales staff. }
                \item { Quality control and assurance product management. }
                \item { Sales revenue management. }
            \end{itemize}
        }
        \item { Project: \textbf{Marketing Platform}, team size: 10. Collaborating with Ukrainian developers to develop marketing systems for business development. }
        \item { Project: \textbf{Affiliate Manager Management (AMM)}, team size: 10 }
        {
            \begin{itemize}
                \item { Building an affiliate management system. }
                \item { Managing advertised products. }
                \item { Managing revenue/commissions of affiliates. }
                \item { Building a product sales strategy. }
                \item { Managing KPIs (Key Performance Indicators) for each affiliate. }
                \item { Managing SLAs (Service Level Agreements) for each affiliate. }
            \end{itemize}
        }
        \item { Project: \textbf{Straight Sale (SS)}, team size: 8 }
        {
            \begin{itemize}
                \item { E-commerce web application, allowing customers to purchase products and make payments through various online payment methods. }
                \item { Integrated payment through Bao Kim Payment. }
                \item { Integrated payment through WooCommerce. }
                \item { Integrated payment through 2C2P. }
                \item { Integrated payment through QR code service Siam Commercial Bank (SCB). }
            \end{itemize}
        }
        \item { Project: \textbf{CRM}, team size: 5 }
        {
            \begin{itemize}
                \item { Customize Axelor opensource. }
                \item { Managing all leads within the system. }
                \item { Managing lead quality. }
                \item { Managing revenue by individual lead. }
                \item { Managing purchase history of each lead. }
                \item { Managing successful delivery history of each lead. }
            \end{itemize}
        }
        \item {Responsibilities: }
        {
            \begin{itemize} % Item(s)
                \item { Develop new applications, components and functions for existing systems. }
                \item { Investigating alternate configurations and implementing better solutions. }
                \item { Building a reporting system for finance and accounting departments. }
                \item { Working with last-mile and multi-national fulfillment units on API integration. }
                \item { Working with online payment providers for API integration. }
                \item { Analyzing customer behavior to find solutions for improving sales quality. }
                \item { Participated in consulting the process of building a data warehouse. }
            \end{itemize}
        }
        \item {Skills: Microservices · RabbitMQ · Redis · Asterisk · FreePBX · VOIP · Apache Kafka (Stream) · Spring Boot · Gin Framework · Gorm Framework · Spring Framework · Spring Security · Java · Golang · Jenkins · Angular · ReactJS · MySQL · PostgreSQL}
      \end{cvitems}
    }
